FTLR proof cases

### 2018-06-21 fully-abstract-comp/ftlr-proof-cases.tex
FTLR register file safety case done.

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  TODO: update...
  By general induction on $n$, i.e. we can assume that the lemma already holds for $n' < n$.

@@

  \lau{TODO: look through this case and find the place where the ''no seal cross boundary thing'' should have been used.}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump.
    If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.}
  and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.}.
  as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n']{(\reg_S(r_i),\reg_T(r_i))} \in \lrr(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrv$ we get
  $\npair[n'-1]{\stpair[.]{c_2}{c_2'}} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

@@

  By Lemma~\ref{lem:nsub-and-nsup-std} and the safety assumption on the register-file, there exists $S \supseteq [\baddr_\stk, \eaddr_\stk]$ such that for some $R : S \fun \powerset{\nats}$ we have $\biguplus_{r \in S} R(r) \supseteq [\baddr_\stk,\eaddr_\stk]$ and for all $r$ in $S$ $\pwfree[W_{R,1}](r).H \nequal \stdreg{R(r),\gc}{\pur}.H$ and $|R(r)| = 1$ and $\pwfree[W_{R,1}](r) \text{ is address-stratified}$.
  Now define
  \[
    W_{R,1}' = W_{R,1}[\free.R^{-1}([\aaddr_\stk,\eaddr_\stk]) \mapsto \revoked][\priv.r_\var{priv\_stk} \mapsto (\stareg[(\ms_{\stk\_\priv,S},\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}),\gc]{\spa,\square},\aaddr+\calllen)]
  \]
  For a fresh $r_\var{priv\_stk}$.
  We know $W_{R,1}' \future W_{R,1}$ as the revoked regions must have been $\spatial$ in $W_{R,q}$ (as they are owned by the part of the world assigned to the stack-register in the register-file relation).
  The static region for the private stack is an extension.

  Pick this world as $W'$ in Eq~\ref{eq:ftlr:call:sealed-code-assump}
  . Let $W_{R,2}'$ be the same world but
  with the ownership of $W_{R,2}$ and pick it for $W_o$.
  Now use monotonicity of $H_\sigma$ with the above facts to get
  \[
    \npair[n']{c_1,c_2,c_1',c_2'} \in \lrexj(W_{R,1}'\oplus W_{R,2}')
  \]
  Now pick register files and memories such that they form $\Phi_S''$ (defined in
  the assumptions) and $\Phi_T''$ and for $W_R'$ and $W_M'$ (we define them below) show
  \begin{enumerate}[label=\roman*.]
  \item \label{case:ftlr:scall:world} $W_{R,1}'\oplus W_{R,2}' \oplus W_R' \oplus W_M'$
  \item \label{case:ftlr:scall:reg} $\npair[n'-1]{(\Phi_S''.\reg,\Phi_T''.\reg)} \in \lrr(\{\rdata\})(W_R')$
  \item \label{case:ftlr:scall:mem} $\memSat[n'-1]{\Phi_S''.\mem,\Phi_S''.\stk,\Phi_S''.\ms_\stk,\Phi_T''.\mem}{W_M'}$
  \end{enumerate}
  to get
  \[
    \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  as desired. It remains to show \ref{case:ftlr:scall:world}-\ref{case:ftlr:scall:mem}.

@@

  Case \ref{case:ftlr:scall:reg}: We need to split the ownership of $W_R'$.
  From assumption $\npair[n'-1]{(\reg_S\update{r}{z},\reg_T\update{r}{z})} \in \lrr(W_R)$, we get a way to split the ownership of $W_R$.
  We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
  region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
  Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
  Finally, $\rretc$ maps to a world with the ownership of $W$.

  we split the world in the same way for the registers that remain unchanged, the
  result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
  This leaves the following cases:
  \begin{description}
  \item[Case $\rstk$:] Show:
    \[
      \npair[n'-1]{(\stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1},((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1))} \in \lrv(W_{R,\rstk}')
    \]
    We know by Assumption~\ref{item:reg-ass}, we know
    \[
      \npair[n']{(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk},((\rw, \linear), \baddr_\stk ,\eaddr_\stk, \aaddr_\stk)} \in \lrrg{\trust}(W_{R,\stk})
    \]
    which by the $\stackReadCond{}$ gives $S \subseteq
    \addressable{\linear,\pwfree}$ and $R : S \fun \powerset{\nats}$.
    We need to pick an $S'$ to argue
    \[
      \npair[n'-1]{[\baddr_\stk,\aaddr_\stk-1]} \in \stackReadCond{W_{R,\rstk}'}
    \]
    To this end pick $S' = R^{-1}(\left(\bigcup_{r\in S} R(r) \right) \setminus [\aaddr_\stk,\eaddr_\stk])$ and $R'$ to be $R$ limited to $S'$.
    As we exclude all the revoked regions and the ownership otherwise remains the
    same in $W_{R,\rstk}'$ as in $W_{R,\rstk}$, the regions in $S'$ are exactly the same in the new world as they were in $W_{R,\rstk}$.
    So what we need to show follows immediately from
    \[
      \npair[n']([\baddr_\stk,\eaddr_\stk]) \in \stackReadCond{W_{R,\rstk}}
    \]
    and by Lemma~\ref{lem:downwards-closed}.

@@

  \item[Case $r_1$,$r_2$:] The two cases are symmetric, so we just show the $r_1$ case:
    \[
      \npair[n'-1]{(\linCons{c_1},\linCons{\Phi_T(r_1)})} \in \lrv(W_{R,r_1}')
    \]
    Follows from the related register files assumption and Lemma~\ref{lem:lincons-lrv}.

  \item[Case $\rretd$:] We have to show
    \[
      \npair[n'-1]{(\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)},\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)})} \in \lrv(W_{R,\rretd}')
    \]
    where $W_{R,\rretd}'$ is the part of $W_R'$ with ownership over $r_\var{priv\_stk}$.
    From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\sigrets',\_,M(r),\gc}$.
    Further by $\memSat[n']{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one
    $r \in S$ there is a $\mscode' \subseteq \mscode$\footnote{Follows from
      $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) =
      \ta$ and finally that $\mscode$ is part of $\ms_S$.} such that
    \begin{equation}
      \npair[n']{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_)\label{eq:ftlr:rretd:Hcode}
    \end{equation}
    where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
    That is $\mscode'$ contains the call we are considering.
    \lau{TODO: Make the above more precise and possibly put into a lemma (also needed in the next case).}
    Use the $r$ in question as the witness.
    The $\xReadCond{}$ gives us $\pwheap(r) \nequal \codereg{\_,\_,\mscode',\gc}$.
    As it is a pure region, it is also present in the future world we consider.
    We now have to show:
    \begin{enumerate}[label=\alph*)]
    \item for $n'' < n'-1$ we have
      \[\npair[n'']{\left(\array{l}\retptrd(\aaddr_\stk,\eaddr_\stk),\\((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)\endarray\right)}
        \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
        \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretd}')
      \]
      First $\dom(\mscode') \subseteq \ta$ follows from \ref{eq:ftlr:rretd:Hcode} and the assumption $[\baddr,\eaddr] \ subseteq \ta$.
      Now pick $r_\var{priv\_stk}$ as the witness.
      We immediately get $\dom(\ms_{\stk\_\priv,S}) = \dom(\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}) = [\aaddr_\stk,\eaddr_\stk]$.
      Next, $\decInstr(\mscode'(\aaddr,\aaddr+\calllen-1)) = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ follows from $\callCond{\Phi_S,r_1,r_2,\aaddr}$.
      Finally, $\ms_\code(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr}$ with $\sigma' = \sigma_\baddr + \offpc \in \sigrets'$ which follows from $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$ and the fact that the call is there.
    \item $\isLinear{\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}}$ iff
      $\isLinear{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk)}}$\\
      Trivial as both are linear.
    \item
      \[
        \begin{array}{l}
          \forall W'' \future \purePart{W_{R,\rretd}'}, W_o, n'' < n'-1,\\
          \quad\npair[n'']{(\vsc_S',\vsc_T')}
          \in  H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
          \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
          \qquad\npair[n']{\retptrd(\aaddr_\stk,\eaddr_\stk),\vsc_S',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1),\vsc_T'} \in
          \lrexj(W'\oplus W_o))
        \end{array}
      \]
      Trivial as both configuration fails.
    \end{enumerate}

>>>>

\begin{lemma}
  \label{lem:ftlr-internal-lemma}
  If
  \begin{itemize}
  \item One of the following sets of requirements holds:
    \begin{itemize}
    \item $\trust = \trusted$, $\Phi_S$ is reasonable up to $n$ steps and $[\baddr,\eaddr] \subseteq \dom(\mscode) = \ta$
    \item $\trust = \untrusted$ and $\npair{[\baddr,\eaddr]} \in \readCond{\lin,W_\pcreg}$
    \end{itemize}
  \item $\Phi_S(\pcreg) = \Phi_T(\pcreg) = ((\rx,\lin),\baddr,\eaddr,\_)$
  \item $\npair{[\baddr,\eaddr]} \in \xReadCond{W_\pcreg}$
  \item $\npair{(\Phi_S.\reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$
  \item $\memSat{\Phi_S.\mem,\Phi_S.\ms_\stk,\Phi_S.\stk,\Phi_T.\mem}{W_M}$
  \item Theorem~\ref{thm:ftlr} holds for all $n' < n$.
  \end{itemize}
  Then
  \[
    \npair{(\Phi_S,\Phi_T)} \in \lro
  \]
\end{lemma}
\begin{proof}
  In the following we will use the following: $\reg_S = \Phi_S.\reg$, $\reg_T = \Phi_T.\reg$, $\ms_S = \Phi_S.\mem$, $\ms_\stk = \Phi_S.\ms_\stk$, and $\stk = \Phi_S.\stk$.

  By general induction on $n$, i.e. we can assume that the lemma already holds for $n' < n$.

@@

  \lau{TODO: look through this case and find the place where the ''no seal cross
    boundary thing'' should have been used. (I have done this, and it does not
    seem necessary (?))}
  In case \ref{case:ftlr:call}, we may assume $r_1 \neq r_2$\footnote{If the register contains a data capability, then the execution fails in the step after the jump.
    If it is an executable capability, then the xjump fails as it does not permit executable capabilities for the data part.}
  and $r_i \neq \pcreg$ for $i \in \{1,2\}$\footnote{The pc is executable which causes the xjump to fail.}.
  as this will cause the execution to fail.
  We need to let the target execution catch up.
  That is $\Phi_T' \nstep[15]{} \Phi_T''$ for
  \[
    \Phi_T'' = \Phi_T
    \begin{array}[t]{l}
      \update{\mem.\aaddr_\stk}{42} \\
      \updReg{\rstk}{((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1)} \\
      \updReg{\rretd}{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)}} \\
      \updReg{\rretc}{\sealed{\sigma',((\perm,\lin),\baddr,\eaddr,\aaddr+\retoffset)}} \\
      \updReg{\rtmp{1}}{0}\\
      \updReg{r_1,r_2}{\linCons{\Phi_T(r_1)},\linCons{\Phi_T(r_2)}}\\
      \updReg{\pcreg}{c_1'}\\
      \updReg{\rdata}{c_2'}
    \end{array}
  \]
  where $\Phi_T(r_i) = \sealed{\sigma,c_i'} \text{ for $i\in\{1,2\}$}$ and $\retoffset = 15$ which is the offset to the return code.
  Now using Lemma~\ref{lem:lro-anti-red-gen} again, it suffices to show
  \[
    \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  By assumption, we have $\npair[n']{(\reg_S(r_i),\reg_T(r_i))} \in \lrrg{\trust}(W_{R,i})$ for some $W_{R,i}$ with $i \in \{1,2\}$.
  We know the capabilities in $r_1$ and $r_2$ are sealed capabilities, and by
  Lemma~\ref{lem:unique-h-sigma} and the definition of $\lrvg{\trust}$ we get
  $\npair[n'-1]{(c_2,c_2')} \in H_\sigma \; \sigma \; \xi^{-1}(W_{R,2})$
  and w.l.o.g.\

@@

  By Lemma~\ref{lem:nsub-and-nsup-std} and the safety assumption on the register-file, there exists $S \supseteq [\baddr_\stk, \eaddr_\stk]$ such that for some $R : S \fun \powerset{\nats}$ we have $\biguplus_{r \in S} R(r) \supseteq [\baddr_\stk,\eaddr_\stk]$ and for all $r$ in $S$ $\pwfree[W_{R,1}](r).H \nequal \stdreg{R(r),\gc}{\pur}.H$ and $|R(r)| = 1$ and $\pwfree[W_{R,1}](r) \text{ is address-stratified}$.
  Now define
  \[
    W_{R,1}' = W_{R,1}[\free.R^{-1}([\aaddr_\stk,\eaddr_\stk]) \mapsto \revoked][\priv.r_\var{priv\_stk} \mapsto (\stareg[(\ms_{\stk\_\priv,S},\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}),\gc]{\spa,\square},\aaddr+\calllen)]
  \]
  For a fresh $r_\var{priv\_stk}$.
  We know $W_{R,1}' \future W_{R,1}$ as the revoked regions must have been $\spatial$ in $W_{R,q}$ (as they are owned by the part of the world assigned to the stack-register in the register-file relation).
  The static region for the private stack is an extension of the old world.

  Pick this world as $W'$ in Eq~\ref{eq:ftlr:call:sealed-code-assump}
  . Let $W_{R,2}'$ be the same world but
  with the ownership of $W_{R,2}$ and pick it for $W_o$.
  Now use monotonicity of $H_\sigma$ with the above facts to get
  \[
    \npair[n']{c_1,c_2,c_1',c_2'} \in \lrexj(W_{R,1}'\oplus W_{R,2}')
  \]
  Now pick register files and memories such that they form $\Phi_S''$ (defined in
  the assumptions) and $\Phi_T''$ and for $W_R'$ and $W_M'$ (we define them below) show
  \begin{enumerate}[label=\roman*.]
  \item \label{case:ftlr:scall:world} $W_{R,1}'\oplus W_{R,2}' \oplus W_R' \oplus W_M'$
  \item \label{case:ftlr:scall:reg} $\npair[n'-1]{(\Phi_S''.\reg,\Phi_T''.\reg)} \in \lrr(\{\rdata\})(W_R')$
  \item \label{case:ftlr:scall:mem} $\memSat[n'-1]{\Phi_S''.\mem,\Phi_S''.\stk,\Phi_S''.\ms_\stk,\Phi_T''.\mem}{W_M'}$
  \end{enumerate}
  to get
  \[
    \npair[n'-1]{(\Phi_S',\Phi_T'')} \in \lro
  \]
  as desired.
  It remains to show \ref{case:ftlr:scall:world}-\ref{case:ftlr:scall:mem}, but first we note that we can deduce the following: From the assumption $\npair{[\baddr,\eaddr]} \in \xReadCond{W}$ we get $R \subseteq \addressable{\normal, \pwheap}$ and $\exists M : S \fun \powerset{\MemSeg}$ such that $\biguplus_{r\in S} \dom(M(r)) \supseteq [\baddr,\eaddr]$ and $\forall r \in S \ldotp \pwheap(r) \nequal \codereg{\sigrets',\_,M(r),\gc}$.
  Further by $\memSat{\ms_S,\stk,\ms_\stk,\ms_T}{W}$, we know that for one $r \in S$ there is a $\mscode' \subseteq \mscode$, call this $r$ for $r_{\mscode'}$,\footnote{Follows from $H^\var{code}$ requiring $\dom(\mscode') \subseteq \ta$ and $\dom(\mscode) = \ta$ and finally that $\mscode$ is part of $\ms_S$.}
  such that
  \begin{equation}
    \npair{(\mscode',\mscode')} \in H^{\var{code}} \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\_,\gsigrets,\gsigcloss)\label{eq:ftlr:rretd:Hcode}
  \end{equation}
  where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$.
  That is $\mscode'$ contains the call we are considering.
  This also entails
  \begin{equation}
    \label{eq:ftlr:code-comp-jud}
    \sigrets',\sigcloss' \vdash_\var{code\_comp} \mscode'
  \end{equation}
from \ref{eq:ftlr:rretd:Hcode} we also get
\begin{itemize}
\item $\dom(\mscode') \subseteq \ta$

  Otherwise we would have $\dom(\mscode') \# \ta$ which would contradict $\dom(\mscode') \subseteq \dom(\mscode) \subseteq\ta$

\item $\sigrets' \subseteq \gsigrets$

  Follows from the above.
\end{itemize}
  \lau{TODO: Make the above more precise and possibly put into a lemma (also needed in the next case).}

@@

  Case \ref{case:ftlr:scall:reg}: We need to split the ownership of $W_R'$.
  From assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrr(W_R)$, we get a way to split the ownership of $W_R$.
  We take this as the starting point, but with the following changes: regions $r_1$ and $r_2$ maps to worlds with no ownership (i.e.\ $\purePart{W_{R,1}'}$).
  region $\rstk$ maps to a world with the same ownership, but of course without the now revoked regions.
  Region $\rretd$ maps to a world that owns private $r_\var{priv\_stk}$ region.
  Finally, $\rretc$ maps to a world with the ownership of $W$.

  we split the world in the same way for the registers that remain unchanged, the
  result follows from Lemma \ref{lem:downwards-closed} and \ref{lem:monotonicity}.
  This leaves the following cases:
  \begin{description}
  \item[Case $\rstk$:] Show:
    \[
      \npair[n'-1]{(\stkptr{\rw,\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1},((\rw,\linear),\baddr_\stk,\aaddr_\stk-1,\aaddr_\stk-1))} \in \lrv(W_{R,\rstk}')
    \]
    We know by Assumption $\npair[n]{(\Phi_S.reg,\Phi_T.\reg)} \in \lrrg{\trust}(W_R)$, we know
    \[
      \npair[n']{(\stkptr{\rw,\baddr_\stk,\eaddr_\stk,\aaddr_\stk},((\rw, \linear), \baddr_\stk ,\eaddr_\stk, \aaddr_\stk)} \in \lrvg{\trust}(W_{R,\stk})
    \]
    which by the $\mathit{stackReadCondition}$ gives $S \subseteq \addressable{\linear,\pwfree}$ and $R : S \fun \powerset{\nats}$.
    We need to pick an $S'$ to argue
    \[
      \npair[n'-1]{[\baddr_\stk,\aaddr_\stk-1]} \in \stackReadCond{W_{R,\rstk}'}
    \]
    To this end pick $S' = R^{-1}(\left(\bigcup_{r\in S} R(r) \right) \setminus [\aaddr_\stk,\eaddr_\stk])$ and $R'$ to be $R$ limited to $S'$.
    As we exclude all the revoked regions and the ownership otherwise remains the
    same in $W_{R,\rstk}'$ as in $W_{R,\rstk}$, the regions in $S'$ are exactly the same in the new world as they were in $W_{R,\rstk}$.
    So what we need to show follows immediately from
    \[
      \npair[n']{[\baddr_\stk,\eaddr_\stk]} \in \stackReadCond{W_{R,\rstk}}
    \]
    and by Lemma~\ref{lem:downwards-closed}.

@@

  \item[Case $r_1$,$r_2$:] The two cases are symmetric, so we just show the $r_1$ case:
    \[
      \npair[n'-1]{(\linCons{c_1},\linCons{\Phi_T(r_1)})} \in \lrv(W_{R,r_1}')
    \]
    Follows from the related register files assumption and Lemma~\ref{lem:lincons-lrv} and the fact that for sealed capabilities if they are in $\lrvg{\trusted}$, then they are in the $\lrv$ part.

  \item[Case $\rretd$:] We have to show
    \[
      \npair[n'-1]{(\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)},\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)})} \in \lrv(W_{R,\rretd}')
    \]
    where $W_{R,\rretd}'$ is the part of $W_R'$ with ownership over $r_\var{priv\_stk}$.

    Use the $r=r_{\mscode'}$ as the witness.
    The $\xReadCond{}$ gives us $\pwheap(r) \nequal \codereg{\_,\_,\mscode',\gc}$.
    As it is a pure region, it is also present in the future world we consider.
    We now have to show:
    \begin{enumerate}[label=\alph*)]
    \item for $n'' < n'-1$ we have
      \[\npair[n'']{\left(\array{l}\retptrd(\aaddr_\stk,\eaddr_\stk),\\((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1)\endarray\right)}
        \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
        \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretd}')
      \]
      First, we already know $\dom(\mscode') \subseteq \ta$ and $\sigrets' \subseteq \gsigrets$.
      Now pick $r_\var{priv\_stk}$ as the witness.
      We immediately get $\dom(\ms_{\stk\_\priv,S}) = \dom(\Phi_T''.\mem|_{[\aaddr_\stk,\eaddr_\stk]}) = [\aaddr_\stk,\eaddr_\stk]$.
      Next, $\decInstr{\mscode'(\aaddr,\aaddr+\calllen-1)} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}}$ follows from $\callCond{\Phi_S,r_1,r_2,\aaddr}$.
      Finally, $\ms_\code(\aaddr+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr}$ with $\sigma' = \sigma_\baddr + \offpc \in \sigrets'$ which follows from $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$ and the fact that the call is there.
    \item $\isLinear{\sealed{\sigma',\retptrd(\aaddr_\stk,\eaddr_\stk)}}$ iff
      $\isLinear{\sealed{\sigma',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk)}}$\\
      Trivial, both are linear.
    \item
      \[
        \begin{array}{l}
          \forall W'' \future \purePart{W_{R,\rretd}'}, W_o, n'' < n'-1,\\
          \quad\npair[n'']{(\vsc_S',\vsc_T')}
          \in  H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode'
          \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
          \qquad\npair[n']{\retptrd(\aaddr_\stk,\eaddr_\stk),\vsc_S',((\rw,\linear),\aaddr_\stk,\eaddr_\stk,\aaddr_\stk-1),\vsc_T'} \in
          \lrexj(W'\oplus W_o))
        \end{array}
      \]
      Trivial as both configurations fails.
    \end{enumerate}

  \item[Case $\rretc$:]
    We have to show
    \[
      \npair[n'-1]{\left(\array{l}\sealed{\sigma',\retptrc(\baddr,\eaddr,\aaddr +
            \calllen)},\\\sealed{\sigma',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}\endarray\right)} \in \lrv(W_{R,\rretc}')
    \]
    where $W_{R,\rretc}'$ has the ownership of $W$.
    Just as in the previous case, we know that for some region $r$ there exists $\mscode' \subseteq \mscode$ such that: $\pwheap(r) \nequal \codereg{\sigrets',\_,\mscode',\gc}$ where $\sigma' \in \sigrets'$ and $\dom(\mscode') \supseteq [\baddr,\eaddr]$ and $\aaddr + \offpc \in \dom(\mscode')$ and $\sigrets' \subseteq \gsigrets$.
    It follows easily from the definition of $H_\sigma^\var{code}$ that
    \begin{equation}
      \label{eq:code-caps-in-h-sigma}
      \npair[n'']{\left(\array{l}\retptrc(\baddr,\eaddr,\aaddr + \calllen),\\((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)\endarray\right)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_{R,\rretc}')
    \end{equation}
    for $n'' < n'-1$.
    Both capabilities are non-linear, so
    \[
      \isLinear{\retptrc(\baddr,\eaddr,\aaddr + \calllen)}\text{ iff } \isLinear{((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset)}
    \]
    is indeed the case.
    Finally we need to show:
    \[
      \begin{array}{l}
        \forall W'' \future \purePart{W_{R,\rretc}'}, W_o, n'' < n'-1,\\
        \quad  \npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o) \ldotp \\
        \qquad \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
      \end{array}
    \]
    To this end let $W'' \future \purePart{W_{R,\rretc}'}$ and $W_o$ be given s.t.
    $W'' \oplus W_o$ is defined.
    Further, let $\npair[n'']{(\vsc_S',\vsc'_T)} \in H^\mathrm{code,\square}_\sigma \; \sigrets' \; \sigcloss' \; \mscode' \; (\ta,\stkb) \; \sigma' \; \xi^{-1}(W_o)$ be given and show
    \[
      \npair[n'']{\retptrc(\baddr,\eaddr,\aaddr + \calllen),\vsc_S',((\rx,\normal),\baddr,\eaddr,\aaddr + \retoffset),\vsc_T'} \in \lrexj(W''\oplus W_o))
    \]
    Now let $n''' \leq n''$ be given along with $\reg[3]_S$, $\reg[3]_T$, $\ms^{(3)}_S$, $\ms^{(3)}_T$,$\ms^{(3)}_\stk$, $\stk^{(3)}$, $W_R''$, and $W_M''$ such that
    \begin{itemize}
    \item $W'' \oplus W_o \oplus W_R'' \oplus W_M''$ is defined
    \item $\memSat[n''']{\ms^{(3)}_S,\ms^{(3)}_\stk, \stk^{(3)}, \ms^{(3)}_T}{W_M''}$
    \item $\npair[n''']{(\reg[3]_S,\reg[3]_T)} \in \lrr(W_R'')$
    \end{itemize}

    Based on $H_\sigma^\var{code}$, there are three possible values for $\vsc_S'$ and $\vsc_T'$.
    In the first case, $\vsc_S'$ is a $\retptrc$ and $\vsc_T'$ is a capability with permission $\rx$.
    In this case, $\var{xjumpResult}$ will produce failed configurations which are trivially in the observation relation.
    In the next case, it is required that $\sigma' \in \sigcloss'$, but this
    cannot be the case as $\sigma' \in \sigrets'$ and we have $\sigrets',\sigcloss' \vdash_{\mathrm{comp-code}} \mscode'$.
\lau{TODO I think this case should follow from $H^\var{code}$ and the comp-code judgement, but it does not.
      Specifically, the comp-code judgement (for now) does not require $\sigrets'$ and $\sigcloss'$ to be disjoint.}

    This leaves us with one final case, namely $\vsc_S'= \retptrd(\baddr_\stk',\eaddr_\stk')$ and $\vsc_T'=((\rw,\linear),\baddr_\stk',\eaddr_\stk',\baddr_\stk'-1)$.
    Further we know
    \[
      \begin{array}{l}
        \exists r \in \addressable{\linear,\pwpriv[W_o]} \ldotp \pwpriv[W_o](r).H \nequal (\stareg[(\ms_{\priv,S}^{(3)},\ms_{\priv,T}^{(3)}),\gc]{\spao,\square}, \aaddr'+\calllen) \tand \\
        \quad \dom(\ms_{\priv,S}^{(3)}) = \dom(\ms_{\priv,T}^{(3)}) = [\baddr_\stk',\eaddr_\stk'] \tand\\
        \quad \decInstr{\code([\aaddr',\aaddr' + \calllen-1])} = \overline{\scall{\offpc,\offsigma}{r_1}{r_2}} \tand \\
        \quad \code(\aaddr'+\offpc) = \seal{\sigma_b,\sigma_e,\sigma_b} \tand \sigma = \sigma_b + \offsigma \in \sigrets
      \end{array}
    \]
    Call this region $r'$.
    By the above, the fact that the code capability pair is in $H_\sigma^\var{code}$ (\ref{eq:code-caps-in-h-sigma}) and Lemma~\ref{lem:unique-ret-seals}, we get $\aaddr' = \aaddr$.
    This means that $W_M''$ and $W_R''$ have this region.

    We know that the two register-files are related which in particular means that the values in register $\rstk$ are related.
    Now consider the following cases: \lau{TODO: Perhaps make a lemma that says if source fail and target step to fail, then the two configurations are in $\lro$.}
